Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-12 paper/paper.Rmd
optimize feature space clustering intro
clarify mlr3spatiotempcv capabilities

The last method from the \pkg{blockCV} package, "environmental blocking", makes use of *k-means* clustering [@hartigan1979a] in a possibly multivariate space.
The user can select a variable via argument `feature` specifying which levels will be used to create clusters.
Hereby, k-means will use Euclidean distance for cluster creation.
Hence, the selected input variables should be of type numeric.
To avoid a potential bias introduced by features with high variance when selecting multiple features, all features are standardized by default.

@@

Considering the wealth and continuing development of spatial and spatiotemporal partitioning techniques for specific applications, we will refrain from providing a complete account of these algorithms.
At present, \pkg{mlr3spatiotempcv} also supports spatiotemporal partitioning using the versatile CLUTO clustering algorithm [@cluto].
CLUTO is available in R through the \pkg{skmeans} package, which provides an interface to a downloadable compiled library with a restriction to non-commercial uses (see `?ResamplingSptCVCluto` in \pkg{mlr3spatiotempcv} for more information).
With respect to functionality, \pkg{mlr3spatiotempcv} supports two-dimensional clustering based on coordinates and three-dimensional clustering on coordinates and time.
Feature clustering is not supported.

>>>>

The last method from the \pkg{blockCV} package, "environmental blocking", makes use of *k-means* clustering [@hartigan1979a] in a possibly multivariate space.
The user can select a variable via argument `feature` which denotes the variable that will be used to create clusters.
Hereby, k-means will use Euclidean distance for cluster creation.
Hence, the selected input variables should be of type numeric.
To avoid a potential bias introduced by features with high variance when selecting multiple features, all features are standardized by default.

@@

Considering the wealth and continuing development of spatial and spatiotemporal partitioning techniques for specific applications, we will refrain from providing a complete account of these algorithms.
At present, \pkg{mlr3spatiotempcv} also supports spatiotemporal partitioning using the versatile CLUTO clustering algorithm [@cluto].
CLUTO is available in R through the \pkg{skmeans} package, which provides an interface to a downloadable compiled library with a restriction to non-commercial uses (see `?ResamplingSptCVCluto` in \pkg{mlr3spatiotempcv} for more information).
With respect to functionality, \pkg{mlr3spatiotempcv} supports two-dimensional clustering based on coordinates, time or features and three-dimensional clustering on coordinates and time.
